
# Code to generate figures in Chapters 2 and 3

This is the code to generate the plots in Chapters 2 and 3


## Set up the code

```{r cache=FALSE, echo=FALSE}
  knitr::read_chunk('../bin/plot.R')
```

```{r init, eval=FALSE}
```

## Code for Figure \ref{fig:bootstrap-95pct-ub-1processor-1task}
``` {r bootstrap-95pct-ub-1processor-1task, eval=FALSE}
```

## Code for Figure \ref{fig:bootstrap-95pct-ub-1processor-10tasks}, \ref{fig:bootstrap-95pct-ub-1processor-50tasks},  \ref{fig:bootstrap-95pct-ub-1processor-100tasks} \ref{fig:bootstrap-95pct-ub-1processor-150tasks} and \ref{fig:bootstrap-95pct-ub-1processor-200tasks}
Same as that for Figure \ref{fig:bootstrap-95pct-ub-1processor-1task} but with
`num.tasks` set to 10, 50, 100, 150 and 200 respectively.

## Code for Figure \ref{fig:sched-1task-1inst}

``` {r sched-1task-1inst, eval=FALSE}
```

## Code for Figure \ref{fig:sched-3task-2inst}

``` {r sched-3task-2inst, eval=FALSE}
```

# Code for schedulr R package

This is the code for the schedulr R package

```{r echo=FALSE, eval=TRUE, include=FALSE}

  library(RCurl)
  library(knitr)

  filename <- 'code.r'
  if (file.exists(filename)) file.remove(filename)

  curlPerform(url = "https://raw.githubusercontent.com/niranjv/schedulr/develop/R/simulated-annealing.R",
              writefunction = function(txt, ...) {
                                   cat(txt, "\n", file=filename, append=T)
                                   return(TRUE)
                              })

  read_chunk(path=filename, labels=c('all'))
  on.exit(unlink(filename))
```

```{r eval=FALSE}
  <<all>>
```

# Colophon

* This document was written mostly in R Markdown (v2) format
(http://rmarkdown.rstudio.com) and LaTex and is an example of a dynamic document for
reproducible research
* Atom (v0.187.0) was used as the text editor and R Studio IDE (v0.99.292) was
used to manage R packages and run R code
* `knitr` (v1.9) converted `*.rmd` files -> `*.md` files and generated `*.pdf`
files for plots
* `pandoc` (v1.12.3) converted `*.md` files -> `*.tex` files
* `bookdown` was used to configure options for `*.tex` files
* `xelatex` (v3.14159265-2.6-0.99991) converted `*.tex` files -> `*.pdf` files
and combined all `*.pdf` files into the final PDF file
* Appendix A was created automatically by pulling the latest version of
the R code from the `schedulr` GitHub repository
(https://github.com/niranjv/schedulr/blob/develop/R/simulated-annealing.R) every
time the PDF file was generated
* Plots in chapters 2 and 3 were generated by referencing and running code
chunks in Appendix B
* GitHub was used for source code management and revision control
(https://github.com/niranjv/ucscamsms2015)
* Travis CI (http://travis-ci.org/niranjv/ucscamsms2015) automatically
re-generated the final PDF file whenever a change was committed to GitHub
* Much of the above workflow was inspired by the one used by Hadley Wickham to
write his *R Packages* book (http://r-pkgs.had.co.nz;
  https://github.com/hadley/r-pkgs)
* The permanent URL for this project is: http://niranjv.github.io/ucscamsms2015/
